\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://inlinkedin.com/in/mtnvk}{\Large Martin Novák}} & Email : \href{mailto:novak9martin@gmail.com}{novak9martin@gmail.com}\\
  \href{https://inlinkedin.com/in/mtnvk}{linkedin.com/in/mtnvk} & Mobile : (+421) 915 382 335 \\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
  \small{Software Engineer with 2+ years of hands-on experience spanning backend development and test automation. Proven track record of delivering scalable Java microservices and optimizing database performance in enterprise environments like Swiss Re and Fiserv. Currently focusing on advancing backend systems engineering with the long-term career goal of transitioning into a software architecture role.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Slovak University of Technology (FEI STU)}{Bratislava, Slovakia}
      {Bachelor's degree in Computer Science}{09/2022 -- 06/2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Swiss Re}{Bratislava, Slovakia}
      {Junior Software Engineer}{12/2023 -- 04/2025}
      \resumeItemListStart
        \resumeItem{Backend Architecture}
          {Engineered and decoupled enterprise Java/Spring Boot microservices responsible for validating inter-entity reinsurance contracts and executing multi-currency financial transactions across global legal entities.}
        \resumeItem{Database Systems \& Performance}
          {Designed and refactored PostgreSQL relational schemas; diagnosed severe performance bottlenecks in legacy migration workflows by identifying N+1 query patterns, consolidating redundant database loops into a unified, high-throughput execution model that significantly reduced migration script runtime.}
        \resumeItem{Cloud Infrastructure \& DevOps}
          {Streamlined application lifecycles by owning and optimizing automated CI/CD pipelines; managed the containerization and seamless deployment of high-availability RESTful APIs to Microsoft Azure environments while implementing automated quality gates.}
        \resumeItem{Reliability \& Quality Engineering}
          {Implemented rigorous automated unit and integration testing pipelines (JUnit, Mockito), establishing robust code coverage targets to prevent regressions in business-critical financial reporting modules.}
      \resumeItemListEnd

    \resumeSubheading
      {IT-Development}{Bratislava, Slovakia}
      {Web Developer}{02/2023 -- 06/2023}
      \resumeItemListStart
        \resumeItem{Frontend Engineering}
          {Maintained and incrementally improved internal Angular applications, resolving UI/UX bugs to optimize vendor workflows for telecommunication asset management.}
        \resumeItem{API Integration \& Data Mapping}
          {Integrated responsive user interfaces with RESTful web services, handling complex data visualization for hardware specifications, real-time antenna status tracking, and infrastructure digital twins.}
      \resumeItemListEnd

    \resumeSubheading
      {Fiserv}{Bratislava, Slovakia}
      {Test Automation Engineer}{06/2022 -- 01/2023}
      \resumeItemListStart
        \resumeItem{Automation Frameworks}
          {Developed automated front-end test suites using Appium and Selenium, increasing testing efficiency by 90\%.}
        \resumeItem{Code Refactoring}
          {Refactored test cases and maintained the framework to improve execution time and ensure reliable CI/CD pipelines via Jenkins.}
        \resumeItem{Documentation}
          {Authored comprehensive technical documentation in Confluence and structured inline code reference guides to facilitate seamless cross-team knowledge sharing.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item \textbf{Languages}{: Java, TypeScript, JavaScript, Python, C, SQL}
   \item \textbf{Frameworks \& Libraries}{: Spring Boot, JPA, Angular, Pandas, NumPy, JUnit, Appium, Selenium}
   \item \textbf{Tools \& Infrastructure}{: Docker, Jenkins (CI/CD), Git, Gradle, JMeter, Azure, Postman, Jira}
   \item \textbf{Languages (Spoken)}{: Slovak (Native), English (C1), German (B1)}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
